Paper 1

### 2022-06-14 scripts/Paper 1.Rmd
update

rm(list = ls())
wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
setwd(wd)
knitr::opts_knit$set(root.dir = wd)
```

@@

```{r read data and some data class cleaning, include=FALSE}
input <- fread("./PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
input <- tidy.csv(input)

@@

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

@@

```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}

(SP.rain <- input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
       #scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
   scale_x_discrete(limits = month.abb) +
  theme_classic()+
  theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-4]
colnames(rainfall_L)[5] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[1] <- "jday"
colnames(rainfall_L)[3] <- "month"
rainfall_L$Site <- "L"
rainfall_L <- rainfall_L %>% filter(month >= 9)

@@

rainfall <- rbind(rainfall_L, rainfall.SP)
rainfall$month <- as.numeric(rainfall$month) 
rainfall$month.abb <- month.abb[rainfall$month]

@@

input.co2fluxes$GPP <- ifelse(input.co2fluxes$GPP < 0 , NA, input.co2fluxes$GPP) # for some reason there were values < 0 for GPP

input.co2fluxes$ERcum_year <- as.numeric(unlist(tapply(input.co2fluxes$ER, input.co2fluxes$Year, cumsum)))
input.co2fluxes$NEEcum_year <- as.numeric(unlist(tapply(input.co2fluxes$Fco2, input.co2fluxes$Year, cumsum)))
input.co2fluxes$GPPcum_year <- as.numeric(unlist(tapply(input.co2fluxes$GPP, input.co2fluxes$Year, cumsum)))

input.co2fluxes$GPP<- ifelse(is.na(input.co2fluxes$GPP), "0", input.co2fluxes$GPP) # replace NA with 0 for cumsum

(NEE <- plot_ly(input.co2fluxes, x = ~jday, y = ~NEEcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))

(ER <- plot_ly(input.co2fluxes, x = ~jday, y = ~ERcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))

(GPP <- plot_ly(input.co2fluxes, x = ~jday, y = ~GPPcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))

>>>>

rm(list = ls())
#wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
#setwd(wd)
#knitr::opts_knit$set(root.dir = wd)
```

@@

```{r read data and some data class cleaning, include=FALSE}
input <- fread("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data/PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
input <- tidy.csv(input)

@@

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

@@

```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
(SP.rain <- input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
       #scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
   scale_x_discrete(limits = month.abb) +
  theme_classic()+
  theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-4]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[1] <- "jday"
colnames(rainfall_L)[3] <- "month"
rainfall_L$Site <- "L"
rainfall_L <- rainfall_L %>% filter(month >= 9)
rainfall_L$month <- as.numeric(rainfall_L$month) 
rainfall_L$month<- month.abb[rainfall_L$month]

@@

rainfall <- rbind(rainfall_L, rainfall.SP)

@@
